Three Algorithms for Merging Navigable Graphs

### 2025-04-23 paper/main.tex
update section Neighborhood Construction Strategies

Various strategies exist for selecting a node's neighborhood. Our merging algorithms are agnostic to the specific neighborhood construction method, which can be provided as a parameter.

@@

>>>>

Various strategies exist for selecting a node's neighborhood. Our merging algorithms are agnostic to the specific neighborhood construction method, which can be provided as a parameter. Here below Algorithm~\ref{alg:knntrategy} and Algorithm~\ref{alg:rngstrategy} are example of possible neighborhood construction functions.

@@

\textsc{KNN-Neighborhood-Construction}(Algorithm~\ref{alg:knntrategy}) is a simplest way to form neighbors, while \textsc{RNG-Neighborhood-Construction} (Algorithm~\ref{alg:rngstrategy}) is more advanced, that paratactically provides better navigability property.
